### 2015-03-01 manuscript/plos_template.tex
prepared signature list figures

\begin{figure*}[b]
\centering
\includegraphics[width=10cm,height=10cm]{APOBEC_two5prime.eps}
\caption{The intensities at two 5' base to the mutated site for 14 mutation signatures categorized as signature 2}
\label{nature2013_sig_apobec}
\end{figure*}

>>>>

\begin{figure*}[b]

\subfigure[APOBEC signature list]{%
  \includegraphics[width=16cm,height=7.5cm]{signatureList_APOBEC.eps}
  \label{APOBEC_sig_list}}

\subfigure[POLE signature in the previous study]{%
  \includegraphics[width=7.5cm,height=7.5cm]{APOBEC_two5prime.eps}
  \label{APOBEC_twofive}}

\caption{The intensities at two 5' base to the mutated site for 14 mutation signatures categorized as signature 2}
\label{nature2013_sig_apobec}
\end{figure*}

\begin{figure*}[b]

\subfigure[POLE1 signature list]{%
  \includegraphics[width=8cm,height=2.5cm]{signatureList_POLE1.eps}
  \label{POLE1_sig_list}}

\subfigure[POLE2 signature list]{%
  \includegraphics[width=8cm,height=2.5cm]{signatureList_POLE2.eps}
  \label{POLE2_sig_list}}

\subfigure[UV signature list]{%
  \includegraphics[width=8cm,height=2.5cm]{signatureList_UV.eps}
  \label{UV_sig_list}}

\subfigure[LMST signature list]{%
  \includegraphics[width=8cm,height=2.5cm]{signatureList_LMST.eps}
  \label{LMST_sig_list}}

\caption{The intensities at two 5' base to the mutated site for 14 mutation signatures categorized as signature 2}
\label{nature2013_sig_apobec}
\end{figure*}
